---
title: "git-resources"
author: "Lennart Wittkuhn"
format: 
  html:
    toc: true
    toc-depth: 3
    toc-title: Contents
    page-layout: full
    code-fold: true
    code-summary: "Show the code"
    link-external-newwindow: true
---


This website lists resources to learn version control of digital objects using [Git](https://git-scm.com/) and [DataLad](https://www.datalad.org/).
The source repository can be found [on GitHub](https://github.com/lnnrtwttkhn/git-resources).

::: {.callout-tip}
## This website is under continous development! 🏗 🚧 👷‍♂️
If you notice any errors or have suggestions for improvements, please either [open an issue](https://github.com/lnnrtwttkhn/git-resources/issues) or contact [Lennart Wittkuhn](mailto:lennart.wittkuhn@uni-hamburg.de).
You can also review the data and all of the source code in [this GitHub repository](https://github.com/lnnrtwttkhn/git-resources).
Thank you!
:::

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(magrittr)
library(data.table)
library(DT)
```

```{r}
create_link_text = function(link, text) {
  link_text = sprintf("<a href='%s' target='_blank'>%s</a>", link, text)
}
```

```{r}
create_html_table = function(dt) {
  DT::datatable(
    dt,
    class = "cell-border stripe", rownames = FALSE, escape = FALSE,
    options = list(
      scrollX = TRUE,
      pageLength = 5,
      lengthMenu = c(5, 10, 15, 20)
    ),
  )
}
```

```{r}
load_data = function(path) {
  data = data.table::rbindlist(lapply(path, data.table::fread))
}
```

```{r}
create_table = function(dt_in) {
  dt_out = dt_in %>%
    .[, link := create_link_text(link = link, text = "Link")] %>%
    .[, source := create_link_text(link = source, text = "Source")] %>%
    setorder(., category, -year)
}
```

# Git

```{r}
dt_git = load_data(Sys.glob(here::here("git-resources.csv")))
dt_git_show = create_table(dt_git)
create_html_table(dt_git_show)
```

# DataLad

```{r}
dt_git = load_data(Sys.glob(here::here("datalad-resources.csv")))
dt_git_show = create_table(dt_git)
create_html_table(dt_git_show)
```